Awareness and Experience of Developers to\\ Outdated and License-incompatible Code on Stack Overflow:\\ An Online Survey

### 2017-11-07 cloverflow_technical_report/cloverflow_survey_rn.tex
Fixed the last FIXME.

\FIXME{Merge changes to the bib file from the TSE version.}

@@

\subsubsection{The answerer survey} 
We selected the participants for our answerer survey based on their Stack
Overflow reputations. On Stack Overflow, a user's reputation reflects how much
the community trusts the user. A user earns reputation when he or she receives
upvotes for good questions and useful answers. \FIXME{I don't understand the
	sentence. @Jens Ok now?:} For example, they gain reputation when they receives an upvote for
their question (+5), an upvote for their answer (+10), or a marking as accepted answer (+15)\footnote{Stack
	Overflow Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site.

>>>>

%\FIXME{Merge changes to the bib file from the TSE version.}

@@

\subsubsection{The answerer survey} 
We selected the participants for our answerer survey based on their Stack
Overflow reputations. On Stack Overflow, a user's reputation reflects how much
the community trusts the user. A user earns reputation when he or she receives
upvotes for good questions and useful answers. For example, they gain reputation when they receive an upvote for
their question (+5) or their answer (+10), or when their answer is accepted (+15)\footnote{Stack
	Overflow Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site.
